Draft TLF generator

### 2023-04-28 posts/manipulate/draft_tlf_generator.qmd
Update draft_tlf_generator.qmd

      invisible(self)
    },
    remove = function(outputs) {
      #check the outputs if exsit firstly
      rm(list = outputs, envir = self$tlfs)
      invisible(self)
    }
  )
)
```
#### Used functions

>>>>

      invisible(self)
    },
    remove = function(outputs) {
      #check the outputs if exsit firstly
      #checkmate::wf(exsit(outputs, envir = self$tlfs))?
      rm(list = outputs, envir = self$tlfs)
      invisible(self)
    }
  )
)
```
#### Used functions
